A survey of HTTP caching options on the open Web

### 2014-12-17 sanity/paper1.tex
small change
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@907 43ef1190-90fd-4dd7-a769-d0121f02b80e

In spite of this, we have not seen it in widespread use, and therefore
we decided to conduct a survey to investigate the actual compliance to
RFC7234 and RFC7232. Our reasons to do this include
\begin{enumerate}
\item Understand the actual usage rather than rely on anecdotal
  conceptions.
\item Encourage the implementation of these mechanisms in Semantic Web
  infrastructure.
\item Point out future research directions.
\end{enumerate}

>>>>

In spite of this, we have not seen it in widespread use in the
Semantic Web, and therefore we decided to conduct a survey to
investigate the actual compliance to RFC7234 and RFC7232. Our reasons
to do this include
\begin{enumerate}
\item Understand the actual usage rather than rely on anecdotal
  conceptions.
\item Encourage the implementation of these mechanisms in Semantic Web
  infrastructure.
\item Point out future research directions.
\end{enumerate}
